### 2019-08-20 maciek.tex
Refinement of lower bound writeup

From this point, OPT does not change its configuration, and the adversary continues to issue a request between a node colocated with the pair $(a_1, a_2)$, which we call $x$ (we update $x$ in every iteration, as it gets moved from this place) and any other node with the same color as $x$.
Upon receiving this request, ALG pays for it the cost at least $1$ and it increases its number of clusters that contain non-singleton components by $1$.
This procedure ends when ALG has no more clusters with singleton-only components left or ALG manages to put $d_1, d_2$ or $d_3$ in place of either $x$ or $y$.

>>>>

From this point, OPT does not change its configuration, and the adversary continues to issue a request between $x$ and any other node with the same color as $x$
(note that by $x$ we might denote different node in every iteration, as $x$ is defined as a node colocated with a component $(a_1, a_2)$).
Upon receiving this request, ALG pays for it the cost at least $1$ and it increases its number of clusters that contain non-singleton components by $1$.
This procedure ends when ALG has no more clusters with singleton-only components left or ALG manages to put $d_1, d_2$ or $d_3$ in place of either $x$ or $y$.
